Modern Graph Generators: A Survey

### 2018-10-15 comparison.tex
MInor correction (Arnau's comment 1)

In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique in terms of scope and new tools related to Big Data processing, our classification and comparative strategy would differ as well.

>>>>

In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy would differ as well.
